---
title: "Quarto Basics"
format:
  html:
    code-fold: true
jupyter: python3
---

For a demonstration of a line plot on a polar axis, see @fig-polar.

```{python}
#| label: fig-polar
#| fig-cap: "A line plot on a polar axis"

import numpy as np
import matplotlib.pyplot as plt

r = np.arange(0, 2, 0.01)
theta = 2 * np.pi * r
fig, ax = plt.subplots(
  subplot_kw = {'projection': 'polar'} 
)
ax.plot(theta, r)
ax.set_rticks([0.5, 1, 1.5, 2])
ax.grid(True)
plt.show()
```

We can also add to this hello world qmd with R scripts. Simply start a new cell and change the name python to r and write your code. 


```{r}
x <- seq(from = 0, to = 10, by = 1)
y <- x^2
plot(x, y)
```

Remember that the shortcuts for VSCode and QMDs are different than Rstudio. To insert a new cell use Ctrl + Shift + I. This will also prompt the user to select the language of the code in the cell. 

```{python}
py_arr = np.array([1, 2, 3, 4, 5])
```


```{r}
# renv::install("reticulate")
library(reticulate)
# use_virtualenv("C:/Users/Zachary.Palmore/GitHub/policy/.venv")
use_virtualenv("r-reticulate")
```



```{python}
import numpy as np
py_arr = np.array([1, 2, 3, 4, 5])
for item in py_arr:
  print(item, end=', ')
```


```{r}
reticulate::py_to_r(py_arr)
```